---
title: "Factor Analysis - Wholesale Customer Data"
author: "Rutwik Guntoorkar"
date: "2023-03-17"
output: html_document
---

```{r}
library(psych)
library(readr)
wcdata <- read.csv("/Users/rutwik/Desktop/RBS/Sem 2/Multivariate Analysis/Wholesale customers data.csv")
attach(wcdata)


fit.pc <- principal(wcdata[-1], nfactors=4, rotate="varimax")
fit.pc

#For Eigen Values
fit.pc$values
round(fit.pc$values, 3)

fit.pc$loadings

```
>
After looking at values, we can consider that:
While RC1 shows relation with Milk, Grocery and Detergents_Paper; 
RC2, RC3 and RC4 shows relations only with Frozen, Fresh and Delicassen respectively and individually.

```{r}
# Loadings with more digits
for (i in c(1,3,2,4)) { print(fit.pc$loadings[[1,i]])}
# Communalities
fit.pc$communality
# Rotated factor scores, Notice the columns ordering: RC1, RC3, RC2 and RC4
fit.pc$scores

# Play with FA utilities

fa.parallel(wcdata[-1]) # See factor recommendation
```
>VSS complexity 1 achieves a maximimum of 0.82  with  3  factors
VSS complexity 2 achieves a maximimum of 0.92  with  3  factors
The Velicer MAP achieves a minimum of 0.15  with  2  factors 
BIC achieves a minimum of  5.79  with  2  factors
Sample Size adjusted BIC achieves a minimum of  18.49  with  2  factors
Statistics by number of factors 

```{r}
fa.plot(fit.pc) # See Correlations within Factors
fa.diagram(fit.pc) # Visualize the relationship
vss(wcdata[-1]) # See Factor recommendations for a simple structure

```

